Constant-round Blind Classical Verification of Quantum Sampling

### 2020-08-22 qpip0.tex
Handle more QPIP0 author notes

\begin{lemma}[binding property of $\PiMeasure$]
	\label{lem:urmila-binding}
	Let $\PMeasureStar$ be a $\BQP$ cheating prover for $\PiMeasure$ and $\lambda$ be the security parameter. Under the QLWE assumption, if $\PMeasureStar$ passes the testing round with probability \Ethan{Not precise enough - probability over what? For all $h$ or $pk$?} $1-\negl(\lambda)$, then there exists some $\rho$ so that for all verifier's input $h \in \zo^n$, the verifier's outputs on the Hadamard round is computationally indistinguishable from $M_{XZ}(\rho, h)$.
	\iffalse    
	Suppose that for all $\lambda\in\bbN$ and $h\in\zo^*$ \Ethan{or $\zo^n$?},
	$\PMeasureStar$ passes the testing round with probability $1-\negl(\lambda)$.
	Then, under the QLWE assumption, there exists some $\rho$ so that for all $h$,
	The verifier's output on the Hadamard round is $\negl(\lambda)$-computationally indistinguishable from $M_{XZ}(\rho, h)$.
	\fi
\end{lemma}

@@

There are several problems with using $\PiNaive$ as a $\SampBQP$ protocol. First, since the verifier doesn't get a sample if he had chosen the testing round in Step~\ref{step:c-urmila-in-naive}, the protocol has completeness error at least $1/2$. Moreover, since Protocol~\ref{proto:urmila4} does not check anything on the Hadamard round, a cheating prover can give up passing the testing round and breaks the commitment on the Hadamard round, with only a constant $1/2$ probability of being caught.
However, we can show that \Cref{proto:qpip0_naive} has a binding property similar to \Cref{proto:urmila4}.
Namely, if a cheating prover passes the testing round with overwhelming probability conditioned on it doesn't ``give up" on the 2nd message, then... \Ethan{Word this better}
The intuition of the proof is to construct another $\BQP$ prover $\Pstar$ which, intuitively, uses $\PNaiveStar$'s strategy when it doesn't abort,
otherwise commits with the maximally mixed states.\Ethan{Finish this high level proof sketch}
...in order to use \Cref{lem:urmila-binding}.
We state the theorem and proof in full technical details as below.

\begin{theorem}[binding property of $\PiNaive$]
	\label{lem:naive-qpip0-binding}
	Let $\PNaiveStar$ be a cheating $\BQP$ prover for $\PiNaive$ and $\lambda$ be the security parameter.
	Under the QLWE assumption, \Ethan{Add ``if P satisfies that..."} if conditioned on $\PNaiveStar$ not aborting (ie. $y\ne\bot$) \Ethan{Make even more explicit ie. say not aborting on round 2}, $\PNaiveStar$ passes the testing round with probability $1-\negl(\lambda)$,
	then the verifier's output in the Hadamard round is $O(\eps)$-computationally indistinguishable from $(d, z_{ideal})$. \Ethan{Check if this notation is defined; give reminder even if it is}
\end{theorem}
\begin{proof}
	We first introduce the \emph{dummy strategy} where the prover chooses $\rho$ as the maximally mixed state and executes the rest of the protocol honestly.
	It is straightforward to verify that this prover would be accepted in the testing round with probability $1-\negl(\lambda)$,
	but has negligible probability passing the verification after the Hadamard round.

>>>>

\begin{lemma}[binding property of $\PiMeasure$]
	\label{lem:urmila-binding}
	Let $\PMeasureStar$ be a $\BQP$ cheating prover for $\PiMeasure$ and $\lambda$ be the security parameter. Under the QLWE assumption, if $\PMeasureStar$ passes the testing round with probability $1-\negl(\lambda)$ for all $h$, then there exists some $\rho$ so that for all verifier's input $h \in \zo^n$, the verifier's outputs on the Hadamard round is computationally indistinguishable from $M_{XZ}(\rho, h)$.
	\iffalse    
	Suppose that for all $\lambda\in\bbN$ and $h\in\zo^*$ \Ethan{or $\zo^n$?},
	$\PMeasureStar$ passes the testing round with probability $1-\negl(\lambda)$.
	Then, under the QLWE assumption, there exists some $\rho$ so that for all $h$,
	The verifier's output on the Hadamard round is $\negl(\lambda)$-computationally indistinguishable from $M_{XZ}(\rho, h)$.
	\fi
\end{lemma}

@@

There are several problems with using $\PiNaive$ as a $\SampBQP$ protocol. First, since the verifier doesn't get a sample if he had chosen the testing round in Step~\ref{step:c-urmila-in-naive}, the protocol has completeness error at least $1/2$. Moreover, since $\PiMeasure$ does not check anything on the Hadamard round, a cheating prover can give up passing the testing round and breaks the commitment on the Hadamard round, with only a constant $1/2$ probability of being caught.
However, we can show that $\PiNaive$ has a binding property similar to $\PiMeasure$:
if a cheating prover $\PNaiveStar$, conditioned on it doesn't ``give up" on the second message, passes the testing round with overwhelming probability,
then the output $(d, z)\leftarrow(\PNaiveStar, \VNaive)$ is close to $(d, z_{ideal})$.
Recall the ideal output
$$\begin{cases}
	z_{ideal}=\bot & \text{if } d=\Rej\\
	z_{ideal}\leftarrow D_x & \text{if } d=\Acc
\end{cases}$$
is drawn from the true distribution instead when $\PNaiveStar$ is accepted.
The intuition of the proof is to reduce to \Cref{lem:urmila-binding} by constructing another $\BQP$ prover $\Pstar$ for $\PiMeasure$.
Specifically, $\Pstar$ uses $\PNaiveStar$'s strategy when it doesn't abort, otherwise honestly inputs some default state for the verifier to measure.
We now state the theorem and proof.

\begin{theorem}[binding property of $\PiNaive$]
	\label{lem:naive-qpip0-binding}
	Let $\PNaiveStar$ be a cheating $\BQP$ prover for $\PiNaive$ and $\lambda$ be the security parameter.
	Suppose that conditioned on $\PNaiveStar$ not aborting on the second round (ie. $y\ne\bot$), it passes the testing round with overwhelming probability.
	Under the QLWE assumption, then the verifier's output in the Hadamard round is $O(\eps)$-computationally indistinguishable from $(d, z_{ideal})$.
\end{theorem}
\begin{proof}
	We first introduce the \emph{dummy strategy} where the prover chooses $\rho$ as the maximally mixed state and executes the rest of the protocol honestly.
	It is straightforward to verify that this prover would be accepted in the testing round with probability $1-\negl(\lambda)$,
	but has negligible probability passing the verification after the Hadamard round.
